\documentclass[12pt]{article}

\usepackage[style=ieee]{biblatex}
\addbibresource{main.bib}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\renewcommand*\familydefault{\sfdefault}

\usepackage[dvipsnames]{xcolor}
\usepackage{listings}
\lstdefinelanguage{Ini}
{
    basicstyle=\ttfamily\small,
    columns=fullflexible,
    morecomment=[s][\color{Orchid}\bfseries]{[}{]},
    morecomment=[l]{\#},
    morecomment=[l]{;},
    commentstyle=\color{gray}\ttfamily,
    morekeywords={},
    otherkeywords={=,:},
    keywordstyle={\color{green}\bfseries}
}

\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{\footnotesize Draft}
\cfoot{}
\rfoot{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\title{
      Git Usage Guidelines \\
      \begin{large}
         For Large Software Projects
      \end{large}
}
\date{\today}
\author{Wiebe and Julian Engineering Cooperation}

\begin{document}

\pagenumbering{gobble} % No numbering on title page
\maketitle

\newpage
\pagenumbering{Roman} % Required to be roman until table of contents
\tableofcontents
\newpage
\pagenumbering{arabic} % Required to be arabic after table of contents

\newpage
\section{Introduction}


\pagebreak
\section{Git Usage and Regulations}
\subsection{Git Config}
Because of the versality of development platforms a Git config is published for
every supported development platform. This config is complete and should not be
tampered with. Any issues regarding tampering or wrong usage should be reported
directly to the nearest technical person with a management role.

When a configuration is not correct for specific projects, the reason should be
documented and reported to a technical manager. When permission is granted the
new configuration is permitted for usage within that Git repository and the
technical manager is expected to revise the currently published Git config and
look for improvements.

\paragraph{Config File}
Every property is supported by a rationale. The file version on the first line
should not be changed by hand. When permitted to modify the file, an x should be
added next to the patch fragment of the version, like so: \lstinline{1.2.3x},
this indicates an experimental config. See appendix \ref{appendix:git_config}
for the latest config file.

\printbibliography

\newpage
\begin{appendix}
   \fancyfoot{} % Remove Footer In Appenix

   \section{Git Config File}
   \href{https://example.com}{Click here to view config file online}

   \label{appendix:git_config}
   \begin{lstlisting}[language=Ini]
#### VERSION 0.0.1
[core]
   fileMode: false # FileMode is false to prevent cross-platform issues
#### END OF GIT CONFIG
   \end{lstlisting}
\end{appendix}

\end{document}